Characteristic polynomials of p-adic matrices

### 2017-02-04 charpoly/charpoly.tex
Organization of the paper.

@@

\section{Theoretical study}

@@

>>>>

In Section \ref{sec:theo_study}, we study the
differential of the characteristic polynomial so as
to get optimal information on precision 
and a compact writing of this differential.
Then, in Sections \ref{sec:diffHess} and \ref{sec:diffFrob}
we propose algorithms to compute this differential
either through Hessenberg or going through
some Frobenius normal form.
Finally, we propose in Section \ref{sec:optjagged}
algorithms to compute the optimal precision
coefficient-wise on the characteristic polynomial
and on some eigenvalues along with
numerical evidence of the behaviour of the computation
of the characteristic polynomial.

@@

\section{Theoretical study}
\label{sec:theo_study}

@@

\begin{rem}
Keeping the previous notation, if $U \in GL_n(K),$
then the corresponding quadruple for 
$UMU^{-1}$ is
$(\alpha, UP, U^{t,-1}Q, \chi_M),$
which can be computed in $O(n^\omega)$ operations in $K.$
This is faster than computing $U com(X-M) U^{-1},$
which is, at first sight, in $O(n^4)$ operations in $K.$
\end{rem}
